Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2020-04-08 paper/notes.tex
NOtes about the previous commmit

>>>>

\subsection{Allowing the stopping mechanism to enhance connection making}

As well as affecting branching, there is no reason why I couldn't have the
axonal function also affect connection making. Consider the equation governing
the rate of change of connections.

\begin{equation} \label{eq:dc}
\frac{\partial c_i}{\partial t} =-\alpha c_i +\beta  \left(1 - \sum_{j=1}^{N} c_{j}\right)[a_i]^k.
\end{equation}

If $\beta$ were to be modulated by $1 - f_i$, then connection making would
occur much more strongly in the correct location. Would it be too good I
wonder? Answer: Yes, it's highly effective. To reproduce, set fModulatesBeta
to true, prop\_modulated to 1 and prop\_unmodulated to 0.

\subsection{Allowing the stopping mechanism to reduce connection decay}

An alternative to the above, is to slow down connection decay within the
stopping zone.
